Handling String-Number Conversion in String Constraint Solving

### 2019-11-07 draft.tex
dont what I am doing
polish str-int conv. subsection

	\draw[->] (q0) edge node [below]{$v_1$} (q1) ;
	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$. If we do so, we will conclude that the formula is unsatisfiable under this domain restriction.

However, the formula is satisfiable when $x=``00010"$. The point is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front. In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.  The SFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such SFA. With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits. Although this SFA still has a loop, but it will not create any exponential component because the loop only represents a sequence of `0' that occurs in the prefix of $x$. It will not affect the integer value of $n=\sti{x}$.

@@

More specifically, we first define two functions:

$$\mathsf{epsAfter(k)}::= (0\leq v_0,\ldots, v_k\leq 9) \wedge v_{k+1}=\ldots =v_m = -1$$
$$\mathsf{toNumber(k)}::= (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})$$

Then we can specify the relation between $n$ and the character variables as follows:
$$(n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$

@@

% \section{Evaluation}
%  \label{section:evaluation}
% \todo{copy a few tables from our test site to here}
\input{evaluation}

>>>>

	\draw[->] (q0) edge node [below]{$v_1$} (q1) ;
	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$. If we do so, we will conclude that the formula is unsatisfiable, because the length of $x$ cannot be $5$  under this domain restriction.

However, the formula is satisfiable when $x=``00010"$. Observe that $\sti{``00010"}=10$. The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front. In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.  The SFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such SFA. With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits. Although this SFA still has a loop, but it will not create any exponential component because the loop only represents a sequence of `0' that occurs in the prefix of $x$. It will not affect the integer value of $n=\sti{x}$.

@@

$$\begin{array}{rl}
\mathsf{epsilonAfter(k)}::=& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
&v_{k+1}=\ldots =v_m = -1\\
\mathsf{toNumber(k)}::=& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
\end{array}
$$

The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$. Recall that we use $-1$ to represent $\epsilon$. The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
Then we can specify the relation between $n$ and the character variables as follows:
$$(n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$ .

@@

% \section{Evaluation}
%  \label{section:evaluation}
% \todo{copy a few tables from our test site to here}

\section{Implementation}
\input{evaluation}
